RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective

### 2022-11-17 main.tex
:speech_balloon: Add TODOs

\begin{document}
% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
% \title{RIScatter: Unifying Backscatter Communication, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% ? Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load switching speed is key for high data rate - symbol ratio is not very large
% TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: general non-adaptive (book) adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% TODO semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence
% * Base e, use 2 in simulation
% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% * (I(X_1;Y_1),I(X_2;Y_2))
% ? Channel estimation error, coordination issues
% TODO  binary input and signal output (BISO) channel, ML figure
\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
	Simulation results demonstrate RIScatter nodes can exploit additional propagation path to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
\end{abstract}

>>>>

\begin{document}
% \title{RIScatter: Unifying Scattering Techniques From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom, AmBC, SR and RIS From a Distribution Perspective}
% \title{RIScatter: Unifying BackCom and RIS From a Probabilistic Perspective}
% \title{RIScatter: Unifying Backscatter Communication, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From a Probabilistic Perspective}
\title{RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface From an Input Distribution Perspective}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% * cooperative input design can be used for co-located RIScatter nodes.
% * hardward to modulate using RIS is already available.
% * RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% ? For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% * Redefine RIS using book
% ? Using RIS to encode is not very interesting as controller is anyway usable
% * Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communication], fast load switching speed is key for high data rate - symbol ratio is not very large
% TODO Beamforming can cancel direct interference to avoid the collapse of noncoherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communication Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * channel coding: general non-adaptive (book) adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% TODO semicoherent: known CSI, unknown primary/backscatter symbols
% * initialization, convergence
% * Base e, use 2 in simulation
% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
% * (I(X_1;Y_1),I(X_2;Y_2))
% ? Channel estimation error, coordination issues
% TODO  binary input and signal output (BISO) channel, ML figure

% ! add table row: adaptive to information source/csi/link weights
% ! explain link weights
% ! add table row: distributions
% ! table to sentences
% ! add primary and backscatter flows to illustrations
% ! discuss table and add challenges in contribution 1
% ! transition challenges (distribution and constellation-adaptive) to contribution 2, 3
% ! think RIScatter applications (use Rui's slides)
\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external radio wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{ris} adapts its phase shift response to enhance or suppress signal strength in specific directions.
	In this paper, we show how both seemingly different technologies and their derivatives can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	Envisioned as a scatter protocol, RIScatter consists of multiple dispersed or co-located passive scatter nodes whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where reflection states are exclusively a function of information symbols (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detection region at the user.
	Simulation results demonstrate RIScatter nodes can exploit additional propagation path to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal difference in active-passive coexisting networks.
\end{abstract}
